Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-04-27 data_appendix_all_years.Rmd
commit

@@

```{r combining household head characteristics with children dataset}
hh_head_2 <- hh_head %>%
  select(female, age, literacy, educ, job, tasks, pov, extr, hh_id) %>%
  rename (female_hhhead = female,
          hhhead_age = age,
          hhhead_literacy = literacy,
          hhhead_educ = educ,
          hhhead_job = job,
          hhhead_tasks = tasks)
total_heads_subset <- hh_head_2 %>% distinct()

@@

@@

#model_simple <- lm(assist ~ floods + droughts + year, data = reg_data)
#summary(model_simple)
model_assist <- lm(assist ~ floods + droughts + age + female + income + child + grandchild + hhhead_educ + female_hhhead + rural + year_factor, data = reg_data)
summary(model_assist)
#model_register <- lm(register ~ floods + droughts + age + female + income + child + grandchild + hhhead_educ + female_hhhead + rural + year_factor, data = reg_data)
#summary(model_register)

>>>>

export_summary_table(dfSummary(total_children))

@@

```{r combining household head characteristics with children dataset}
hh_head_2 <- hh_head %>%
  select(female, age, literacy, educ, job, tasks, pov, extr, hh_id) %>%
  rename (female_hhhead = female,
          hhhead_age = age,
          hhhead_literacy = literacy,
          hhhead_educ = educ,
          hhhead_job = job,
          hhhead_tasks = tasks)

total_heads_subset <- hh_head_2 %>% distinct()

@@

reg_data %>%
  group_by(rural) %>%
  summarise(n = n())

@@

#model_simple <- lm(assist ~ floods + droughts + year, data = reg_data)
#summary(model_simple)
model_assist <- lm(assist ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + rural + year_factor, data = reg_data)
summary(model_assist)
model_register <- lm(register ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + rural + year_factor, data = reg_data)
summary(model_register)
model_reason_t <- (lm(work_reason ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = reg_data))
summary(model_reason_t)
